Type Checker Generation using Reference Attribute Grammars

### 2024-01-04 MSc.tex
Add an initial abstract

\theabstract{
%Your abstract should capture, in English, the whole thesis with focus on the problem and solution in 150 words. It should be placed on a separate right-hand page, with an additional \textit{1cm} margin on both left and right. Avoid acronyms, footnotes, and references in the abstract if possible.
%Leave a \textit{2cm} vertical space after the abstract and provide a few keywords relevant for your report. Use five to six words, of which at most two should be from the title.
}

>>>>

\theabstract{
%Your abstract should capture, in English, the whole thesis with focus on the problem and solution in 150 words. It should be placed on a separate right-hand page, with an additional \textit{1cm} margin on both left and right. Avoid acronyms, footnotes, and references in the abstract if possible.
%Leave a \textit{2cm} vertical space after the abstract and provide a few keywords relevant for your report. Use five to six words, of which at most two should be from the title.

  Static type checkers are a popular method for early detection of bugs in computer programs, by ensuring the correct data types are used throughout the program.
  One approach for implementing type checkers are Reference Attribute Grammars (RAGs), a formalism for specifying the static semantics of programming languages by declaring attributes on an abstract tree-representation of the program, and is used by the JastAdd meta-compilation system.

  This report contains a study on the usability of JastAdd to programmatically generate executable type checkers from syntax-directed typing rules.
  This aims to provide integration with existing compilers implemented with JastAdd, as well as a playground for type systems usable as an educational tool.

  We find RAGs to be a flexible model for syntax-directed typing rules, and our software was able to support simple values, nodes with premises placing demands on their children, and those with rules requiring type variables.
  It proved difficult to provide compile-time verification of the typing rules, and further work is required to extend the compiler to support type environments, a necessity for most real-world type systems.
}
